Want to see if we can get a better waershed using possons `fwaatlasbc` vs`fwapgr` on its own.  Makes sense since
Big Joe Thorley has been working on this for a while.  Lets see if we can get a better watershed for a site of interest.

```{r}
# pak::pkg_install("poissonconsulting/fwatlasbc")

library(fwatlasbc) 
```



```{r}

# grab our site of interest, and add lat lon

site_prep <- fpr::fpr_db_query("SELECT * FROM bcfishpass.crossings_vw WHERE stream_crossing_id = 198934") |> 
  sf::st_transform(4326) |> 
  # fpr::fpr_sp_assign_sf_from_utm(col_easting = "utm_easting", col_northing = "utm_northing", crs_return = 4326) |> 
  fpr::fpr_sp_assign_latlong() |> 
  # we need to drop zM for plotting
  sf::st_zm()

# site_prep2 <- bcfishpass |>
#   dplyr::filter(stream_crossing_id == 198934) |>
#   fpr::fpr_sp_assign_sf_from_utm(col_easting = "utm_easting", col_northing = "utm_northing", crs_return = 4326) |>
#   fpr::fpr_sp_assign_latlong()



t <- site_prep |> 
  sf::st_drop_geometry() |> 
  fwatlasbc::fwa_add_blk_to_lon_lat() |> 
  sf::st_drop_geometry() |>
  dplyr::select(stream_crossing_id, blk, rm, lon, lat)
  

wshed <- t |> 
  dplyr::mutate() |> 
  fwatlasbc::fwa_add_watershed_to_blk()

network <- fwa_add_collection_to_polygon(wshed, "stream_network")


p1 <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = wshed) +
  ggplot2::geom_sf(data = network, color = "blue") +
  ggplot2::geom_sf(data = site_prep, color = "red") +
#  ggplot2::geom_sf(data = rms) +
  NULL
```
lets compare this to the watershed we get with `fwapgr`

```{r}

site_wshd_fwapgr <- site_prep |> 
  fpr::fpr_sp_assign_sf_from_utm(col_easting = "utm_easting", col_northing = "utm_northing", crs_return = 3005) |>
  fpr::fpr_sp_watershed()
  # to map we need to drop Z
  # sf::st_zm()



# network2 <- wshds |> 
#   dplyr::filter(stream_crossing_id == 198934) |> 
#   fwa_add_collection_to_polygon("stream_network")


network2 <- site_wshd_fwapgr |> 
  fwa_add_collection_to_polygon("stream_network")


# p2 <- wshds |> 
#   dplyr::filter(stream_crossing_id == 198934) |> 
#   ggplot2::ggplot() +
#   ggplot2::geom_sf() +
#   ggplot2::geom_sf(data = network2, color = "blue") +
#   ggplot2::geom_sf(data = site_prep, color = "red") 

p2 <- site_wshd_fwapgr |> 
  ggplot2::ggplot() +
  ggplot2::geom_sf() +
  ggplot2::geom_sf(data = network2, color = "blue") +
  ggplot2::geom_sf(data = site_prep, color = "red") 


```
Let's put these two plots side by side to compare

```{r}
cowplot::plot_grid(
  p1, p2
)
```

Now lets "exclude the fundamental watershed in which the start falls" as per the `exclude` param in `fwa_add_watershed_to_blk`


```{r}
wshed3 <- t |> 
  fwatlasbc::fwa_add_watershed_to_blk(exclude = TRUE)

network3 <- fwa_add_collection_to_polygon(wshed, "stream_network")


p3 <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = wshed3) +
  ggplot2::geom_sf(data = network3, color = "blue") +
  ggplot2::geom_sf(data = site_prep, color = "red") +
#  ggplot2::geom_sf(data = rms) +
  NULL

cowplot::plot_grid(
  p3, p2
)
```
<br>

Visualize difference betwwen exclude true and exclude false


```{r}
sf::st_difference(wshed, wshed3) |> 
  ggplot2::ggplot() +
  ggplot2::geom_sf()+
  ggplot2::geom_sf(data = network, color = "blue") +
  ggplot2::geom_sf(data = site_prep, color = "red")
```

