---
title: "dfo_stock_assessment"
date: "Created: 2024-03-07 | Updated: `r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  html_document:
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, dpi=60, out.width = "100%")

options(scipen=999)
options(knitr.kable.NA = '--') #'--'
options(knitr.kable.NAN = '--')
```


We are going to quickly look at what data we have available on salmon in the Upper Bulkley and Morice. We can access the
[NuSEDS-New Salmon Escapement Database System](https://open.canada.ca/data/en/dataset/c48669a3-045b-400d-b730-48aafe8c5ee6)
through the [Open Government Portal](https://open.canada.ca/en) which is actually a CKAN - just like the Skeena Salmon Data Centre.

<br>

Load the packages we need
```{r}
library("rgovcan")
library("ckanr")
library("tidyverse")
library("fpr")


# set up the connection to the data portal
ckanr_setup(url = "https://open.canada.ca/data/en")
```

<br>

Search for the data we want using key words like "Pacific Salmon Conservation Units" and "North and Central Coast NuSEDS".


```{r ckan-search}
nuseds_search <- govcan_search(keywords = c("North and Central Coast NuSEDS"), records = 150, format_results = TRUE) %>% 
  pull(resources) %>% 
  bind_rows()

```


<br>

Have a look at the first 10 records of select columns of the search for "North and Central Coast NuSEDS"
```{r view-ckan-search2}
nuseds_search %>% 
  head(10) %>% 
  dplyr::select(id, description, url, name) %>% 
  fpr::fpr_kable(font = 12)

```

<br>

Download and filter an individual file.  A file called `All Areas NuSEDS.csv.xlsx` looks promising and after initial 
review we can confirm it has our study area in it. `North and Central Coast NuSEDS_20240110.xlsx` probably does too but
guessing that is made from the `All Areas` file so we will skip for now.


Thinking about it - perhaps the `All Areas NuSEDS.csv` is the current version and the rest are designed as archives...
Let's check. Looks as though the `All Areas NuSEDS.csv` is perhaps too big to download straight to memory as we did before (we get a 0 sized tibble).  For this reason we will download the csv by adding the `store = "disk"` param to the `ckan_fetch` call.

```{r csv-dl}
name_csv <- 'All Areas NuSEDS.csv'

study_areas <-  c("BULKLEY", "MORICE", "KISPIOX", "ZYMOETZ", "KITSUMKALUM")

nuseds_search %>% 
  dplyr::filter(name == name_csv) %>% 
  dplyr::pull('url') %>% 
  ckan_fetch(store = "disk", path = paste0('data/inputs_raw/', name_csv)) 

#read it back in  
csv <- read_csv(paste0('data/inputs_raw/', name_csv))

# filter for our study area
nuseds <- csv %>%   
  janitor::clean_names() %>% 
  dplyr::filter(stringr::str_detect(gazetted_name, paste(study_areas, collapse = "|"))) 

nuseds %>% 
  fpr::fpr_kable(font = 12)

```

<br>

Yup - thinking that is what is going on... good to know. **ANOTHER GOOD TO KNOW** is that the `All Areas NuSEDS.csv` file is over 150mb which is waaaay to big for git. We needed to filter it down  to our study area and replace the original file before we want commit to the repo.  Will will do that below

<br>

```{r csv-resize}
nuseds %>% 
  readr::write_csv(paste0('data/inputs_raw/', name_csv))

```


View the data for historic spawner data

```{r}
# have a look at the historic spawner data for the upper Bulkley
spawn <- nuseds %>% 
  dplyr::filter(stringr::str_detect(waterbody, paste(study_areas, collapse = "|")) & 
                  !is.na(natural_adult_spawners) |
                  !is.na(total_return_to_river)) %>% 
  dplyr::arrange(waterbody, species, analysis_yr)

# here is a bit of extra work that may come in handy later
  # keep only rows with non-NA values in the columns with useful info
  # dplyr::filter(if_any(natural_adult_spawners:total_return_to_river, ~ !is.na(.))) %>% 
  # dplyr::filter(if_any(c(natural_adult_spawners:total_return_to_river, 
  #                        starts_with("start"), 
  #                        starts_with("end"), 
  #                        starts_with("peak"),
  #                        starts_with("natural"),
  #                        starts_with("stream"),
  #                        ends_with("presence")), ~ !is.na(.)))


spawn %>% 
  fpr::fpr_kable(font = 12)

```

<br>

Note the results of the following columns since they may feed well into our production of xxxxxxxxxxx:

`r names(spawn) %>% .[str_detect(., '_dt')]`

<br>

Since we are already here let's have a quick look at the data dictionary to see what those columns mean.

```{r get-dict}
dict <- nuseds_search %>% 
  dplyr::filter(name == "Data Dictionary NuSEDS") 
  # pull(url) %>% 
  # ckan_fetch() 

dict %>% 
  dplyr::select(id, description, url, name) %>% 
  fpr::fpr_kable(font = 12)


```

<br>

Ha - looks like there is a duplicate name for the dictionary (french version - cool) that causes our call to ckan_fetch to fail.
Let’s just grab the english one which is first so is kept with the `dplyr::distinct` call.


```{r get-dict2}
nuseds_search %>% 
  dplyr::filter(name == "Data Dictionary NuSEDS") %>% 
  dplyr::distinct(package_id, .keep_all = TRUE) %>% 
  pull(url) %>% 
  ckan_fetch(store = "disk", path = 'data/inputs_raw/data_dictionary_nu_seds.csv') 
```


<br>

Let's have a look at it. Actually - it appears to have `invalid UTF-8` characters in the `Field Definition` column
so we will need to remove those first. 

    Error in sub(re, "", x, perl = TRUE) : input string 106 is invalid UTF-8
    
Seen this before...  Weird little copy and paste characters.  We can deal.

```{r view-data-dict}
dict <- read_csv('data/inputs_raw/data_dictionary_nu_seds.csv')

dict %>% 
  # select(-`Field Definition`) %>% 
  mutate(across(all_of(names(.)), ~str_replace_all(as.character(.), "[^ -~]", ""))) %>% 
  fpr::fpr_kable(font = 12)
```

<br>

lets grab it back and make a plot with the function (`ldfo_sad_plot_line`) newly minted in https://github.com/NewGraphEnvironment/restoration_wedzin_kwa_2024/blob/main/scripts/functions.R


```{r fig-dfo}
source('scripts/functions.R')

# lets grab it back and make a plot with the functionl dfo_sad_plot_line newly minted in `scripts/functions.R`
nuseds |> 
  ldfo_sad_plot_line(region = "ZYMOETZ RIVER - UPPER", 
                     col_y = "total_return_to_river", 
                     col_facet = "species", 
                     col_group = "analysis_yr", 
                     col_group_exclude = "species",
                     value_group_exclude = "Chinook")
```


In order to render this document we need a work around from the standard bookdown method. We run this command below
by hand in the console to render the document.

```{r render-manual, eval = FALSE}
rmarkdown::render("scripts/dfo_stock_assess.Rmd", output_file = "dfo_stock_assess.html", output_dir = "memos")

```

